Formalization, Mechanization and Automation of \\ G\"{o}del's Proof of God's Existence

### 2013-11-01 Talks/FU-Berlin/talk-part-7.tex
Fix images
Change transition images

\begin{transitionframe}{Images/Transitions/TrifidNebula(Nasa)(PublicDomain).jpg}
\textbf{Part F:}

@@

Our novel contributions the  theorem proving community includes \\[.5em]
\begin{itemize}
\item Powerful infrastructure for reasoning with higher-order modal logic using existing proof assistants and HOL provers
\item A new natural deduction calculus for higher-order modal logic
\item Difficult new benchmarks problems for HOL provers
\item Huge media attention
\end{itemize}
\end{frame}

@@

>>>>

\begin{transitionframe}{Images/Transitions/TrifidNebula(Nasa)(PublicDomain).jpg}{black}
\textbf{Part F:}

@@

Our novel contributions to the theorem proving community include \\[.5em]
\begin{itemize}
\item Powerful infrastructure for reasoning with higher-order modal logic using existing proof assistants and HOL provers
\item A new natural deduction calculus for higher-order modal logic
\item Difficult new benchmarks problems for HOL provers
\item Huge media attention
\end{itemize}
\end{frame}

@@

\begin{frame}{Licenses} \centering
\includegraphics[scale=0.5]{Images/CC-BY-SA.png}

\bigskip
\bigskip

\begin{center}
The following images used in these slides were obtained in commons.wikimedia.org and are licensed as follows:

\bigskip

CC-BY-SA:

ReligiousSymbols, PaganReligiousSymbols, NoGod.

\bigskip

Public Domain:

TrifidNebula
\end{center}
\end{frame}
